---
title: "Pre-Work"
bibliography: library.bib
biblio-style: apalike
---

```{r, child="_setup.Rmd"}
```

We can use this space to go ahead and write out any exercise or prework that you would like have done prior to coming.

## Session 1

This plot is generated using ggplot2 [@ggplot2].

```{r}
library(ggplot2)
ggplot(iris, aes(Species, Sepal.Length))+
  geom_col()

```


## Session 2

## Session 3

###Follow-up work###
Here I describe the follow-up work I did for Session 3 wherein I imported a data set using rio(), practiced creating visualisations of that data set with ggplot(), documented those efforts using R Markdown, and published that documentation to my Github website.

First, I loaded the tidyverse and rio packages for managing and importing data into R. 

```{r}
library(tidyverse)
library(rio)
```

Then I imported my data set. In this data set, I explore belief in harmless wrongs (i.e. the belief that certain
behaviors are immoral even if they do not harm) in a sample of users of the website Amazon Mechanical Turk. I tested what proportion of people believe in harmless wrongs or, alternatively, believe that behaviors are only wrong insofar as they cause harm. I also askedpeople who belive in harmless wrongs to provide an example of a harmless wrong, and I measured various perceptions of those harmless wrongs (immoral participants thought those behvaiors were, how indicative those behaviors were of poor moral character, etc.)

```{r}
HarmlessWrongs <- import("Study175bDatasav.sav")
```


After importing the dataset, I checked the data set using the head() function. 

```{r}
head(HarmlessWrongs, 10)
```

I am interested in why people consider harmless wrongs to be immoral. If these behaviors cause no harm, then what is
unethical about them? 

In my data set, I asked people who believe in harmless wrongs to supply an example of a harmless wrong. I also asked these people to indicate precisely how immoral they considered that behavior to be (1 = not at all; 7 = very), and I asked people to rate the behavior on several other dimensions. One of those dimensions was the degree to which participants view the behavior as indicative of poor moral character (1 = not at all; 7 = very much so). 

I am interested whether harmless wrongs are perceived as wrong because they are indicative of poor moral character. Therefore, I created a scatterplot of the relationship between perceptions of harmless wrongs as indicating poor moral character (on the X axis) and perceptions of harmless wrongs as immoral (on the Y axis). I used ggplot's geom_point() geometry.  

```{r}
ggplot (HarmlessWrongs, aes(x = HWpoorcharacter, y = HWHowImmoral)) + geom_point()
```

One limitation of the above visualization is that it does not depict the large numbers of participants with identical responses. Therefore, I created a second visualization using as my geometric object geom_count(). 

```{r}
ggplot (HarmlessWrongs, aes(x = HWpoorcharacter, y = HWHowImmoral)) + geom_count()
```

I also created a box plot visualization. 

```{r}
ggplot (HarmlessWrongs, aes(x = factor(HWpoorcharacter), y = HWHowImmoral)) + geom_boxplot()
```

And I created a violin plot visualization. 

```{r}
ggplot (HarmlessWrongs, aes(x = factor(HWpoorcharacter), y = HWHowImmoral)) + geom_violin()
```


## Session 4

For my follow-up work to Session 4, I worked on the code for importing data directly from Qualtrics using the qualtRics package. I will be collecting data in Qualtrics over multiple time points and thus would like automate the process of downloading and analyzing those data as they come in. 

First, I installed and loaded the qualtRics package. 

```{r}
install.packages("devtools", repos = "http://cran.us.r-project.org")
devtools::install_github("ropensci/qualtRics")
```

```{r}
library(qualtRics)
```

Then I registered my Qualtrics credentials. (I assigned my Qualtrics API token as the value of QualtricsAPIToken within .rprofile to keep it hidden here.) I also told R not to use the labels but rather to use values for survey responses.

```{r}
registerOptions(api_token = QualtricsAPIToken, base_url="wakeforest.ca1.qualtrics.com")
registerOptions(useLabels = FALSE)
```

I think imported the Harmless Wrongs data set directly from Qualtrics using the getSurvey() function. 

```{r}
HarmlessWrongsfromQualtrics <- getSurvey(surveyID = "SV_8IbGxs0unkqqERv", includeQuestionIds = c("HWHowImmoral", "HWpoorcharacter"))
```

I then checked the data set using the head() function. 

```{r}
head(HarmlessWrongsfromQualtrics, 10)
```

I am now able to retrieve data directly from Qualtrics, which will be useful for my SOTL project this semester. I will be asking my students to complete Qualtrics surveys every other week for the entire semester. I hope to write some R code that will download, analyze, and create a report from those data and that I can (re)run at any point in the semester. 

## Session 5

## Session 6

## Session 7

## Session 8

----

## References